---
title: "OBGY_steroid_total_EDA_v4"
output: html_document
date: "2022-10-13"
---

```{r env, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warnings= FALSE)
library(tidyverse)
library(knitr)
library(gtsummary)
library(labelled)
library(summarytools)
library(kableExtra)
library(magrittr)
```

```{r,warning = FALSE, message = FALSE}
source("R_code/find_Preg_Date.R")
source("R_code/cohort_preg_date.R")
source("R_code/split_group.R")
source("R_code/total_EDA.R")

```

# Maternal characteristics


<center> **[Table 1.1] Summary of Maternal characteristics** </center> 
```{r}
mom_df <- demo_df[c(6,9,11,12,20,21,22,23,24,25,26,27)]

mom_df$type <-mom_df$type %>% factor(levels=c("D","A"), labels = c("Labor","Miscarriage"))
mom_df$twin <-mom_df$twin %>% factor(levels=c(0,1), labels = c("No","Yes"))
mom_df$산과력_출산력T_1 <-mom_df$산과력_출산력T_1  %>% factor(levels=c(0,1,2), labels = c("0","1","≥2"))
mom_df$산과력_출산력P_1 <-mom_df$산과력_출산력P_1  %>% factor(levels=c(0,1,2), labels = c("0","1","≥2"))
mom_df$산과력_출산력A_1 <-mom_df$산과력_출산력A_1 %>% factor(levels=c(0,1,2), labels = c("0","1","≥2"))
mom_df$산과력_출산력SA_1<-mom_df$산과력_출산력SA_1 %>% factor(levels=c(0,1,2), labels = c("0","1","≥2"))
mom_df$산과력_출산력AA_1 <-mom_df$산과력_출산력AA_1%>% factor(levels=c(0,1,2), labels = c("0","1","≥2"))
mom_df$산과력_출산력L_1 <-mom_df$산과력_출산력L_1  %>% factor(levels=c(0,1,2), labels = c("0","1","≥2"))
mom_df$group_s <- mom_df$group_s %>% factor(levels = c("Group_Control", "Group_exp_A", "b_prime","b_rest","c_prime","c_rest"))
mom_df$GA <-as.numeric(mom_df$GA)

var_label(mom_df) <- list(group_s = "Group", type = "Type", age = "Age", GA = "Gestational wks of delivery", twin = "Twin", 산과력_출산력T_1 = "Parity_T",산과력_출산력P_1 = "Parity P", 산과력_출산력A_1 = "Parity A", 산과력_출산력AA_1 = "Parity AA",산과력_출산력SA_1 = "Parity SA", 산과력_출산력L_1 = "Parity L")


print(dfSummary(mom_df, plain.ascii = FALSE, style = "multiline", graph.magnif = 0.75, varnumbers=FALSE, valid.col = TRUE, display.labels=TRUE,
                headings=FALSE), method = 'render')

theme_gtsummary_compact()
```

<center> **[Table 1.2] descriptive statistics of Maternal characteristics** </center>
```{r}
mom_df %>% 
  tbl_summary(by = group_s, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  modify_spanning_header("stat_1"~ "대조군", c("stat_2","stat_3","stat_4","stat_5","stat_6") ~ "실험군") %>%
  bold_labels()

theme_gtsummary_compact()
```

## Continuous
<center> **[Table 1.3] descriptive statistics of Maternal characteristics** </center>
```{r}
stby(mom_df[,c(3,4)], mom_df$group_s, descr,stat="common") %>%
  tb(order = 3) %>%
  kable(digits=1, format="html")  %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(table.envir = "ctable", font_size = 17, full_width = F)

theme_gtsummary_compact()
```


# Steroid
<center> **[Table 1.4] 그룹별 사용한 스테로이드 약제 비율표 ** </center>
```{r result="asis"}
table_steroid$group_s <- table_steroid$group_s %>% factor(levels = c("Group_Control", "Group_exp_A", "b_prime","b_rest","c_prime","c_rest"))

table_steroid %>% 
  select(steroid_name,group_s) %>% 
  tbl_summary(by = group_s,  
              digits = all_categorical() ~2,
              label = steroid_name ~"처방한글명") %>% 
  bold_labels()

theme_gtsummary_compact()
```

# Comrbidity
<center> **[Table 1.5] 임신 1년전부터 임신종결일까지 진단받은 동반질환 비율표 ** </center>
```{r result="asis"}
p_diag_total$group_s <- p_diag_total$group_s %>% factor(levels = c("Group_Control", "Group_exp_A", "b_prime","b_rest","c_prime","c_rest"))

p_diag_2 = p_diag_total[,c(13:43)]
p_diag_2 %>% 
  tbl_summary(by=group_s,
              missing_text = "(Missing value)", 
              digits = all_categorical() ~ c(1, 2)) %>%
  add_p(
     pvalue_fun = ~style_pvalue(., digits = 3)) %>%
    # test = list(all_categorical()~"chisq.test"))%>%
  add_overall() %>% 
  bold_labels()

theme_gtsummary_compact()
```

# Neonatal Outcome
<center> **[Table 1.6] Summary of Neonatal outcome** </center> 
```{r}
n_baby_total <- n_baby_total[-c(1,8,10,11,32)]

n_baby_total$유도분만 <-n_baby_total$유도분만 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$성별 <-n_baby_total$성별 %>% factor(levels=c(0,1), labels =c("Female","Male"))
n_baby_total$감염정보_유무 <-n_baby_total$감염정보_유무 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$수직감염_유무 <-n_baby_total$수직감염_유무 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$Maternal.Antenatal.History_유무 <-n_baby_total$Maternal.Antenatal.History_유무 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$분만형태_코드 <-n_baby_total$분만형태_코드 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$Apgar.Score1_v2 <-n_baby_total$Apgar.Score1_v2  %>% factor(levels=c(0,1), labels =c("No(<7)","Yes(≥7)")) 
n_baby_total$Apgar.Score5_v2 <-n_baby_total$Apgar.Score5_v2 %>% factor(levels=c(0,1), labels =c("No(<7)","Yes(≥7)"))
n_baby_total$PROM <-n_baby_total$PROM %>%factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$태변착색 <-n_baby_total$태변착색 %>%factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$True.knot <-n_baby_total$True.knot %>%factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$Nuchal.cord <-n_baby_total$Nuchal.cord %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$산소흡입 <-n_baby_total$산소흡입 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$심폐소생술.유무 <-n_baby_total$심폐소생술.유무 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$머리 <-n_baby_total$머리 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$얼굴 <-n_baby_total$얼굴%>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$눈 <-n_baby_total$눈 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$제대 <-n_baby_total$제대 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$근골격계 <-n_baby_total$근골격계 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$위장관계 <-n_baby_total$위장관계 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$비뇨기계 <-n_baby_total$비뇨기계 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$생식기계 <-n_baby_total$생식기계 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$신경계 <-n_baby_total$신경계 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$병실 <-n_baby_total$병실 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_total$치료결과 <-n_baby_total$치료결과 %>% factor(levels=c("48시간 이내사망", "48시간 이후사망", "경쾌", "완쾌", "진단만", "치료안함", "호전안됨"), labels =c("48시간 이내사망", "48시간 이후사망", "경쾌", "완쾌", "진단만", "치료안함", "호전안됨"))
n_baby_total$출생시체중 <-as.numeric(n_baby_total$출생시체중)
n_baby_total$재원기간  <-as.numeric(n_baby_total$재원기간)
n_baby_total$태반_중량  <-as.numeric(n_baby_total$태반_중량)
n_baby_total$태반_길이 <-as.numeric(n_baby_total$태반_길이)

n_baby_total$group_s <- n_baby_total$group_s %>% factor(levels = c("Group_Control", "Group_exp_A", "b_prime","b_rest","c_prime","c_rest"))

var_label(n_baby_total) <- list(group_s = "Group", Apgar.Score1_v2 = "apgar score≥7 (1min)", Apgar.Score5_v2="apgar score≥7 (5min)", 
                          태반_중량 = "태반중량(g)", 출생시체중 = "출생시체중(kg)")


print(dfSummary(n_baby_total, plain.ascii = FALSE, style = "multiline", graph.magnif = 0.75, varnumbers=FALSE, valid.col = TRUE, display.labels=TRUE,
                headings=FALSE), method = 'render')

theme_gtsummary_compact()
```

<center> **[Table 1.7] descriptive statistics of Neonatal outcome** </center>
```{r}
n_baby_total%>% 
  tbl_summary(by = group_s, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  modify_spanning_header("stat_1"~ "대조군", c("stat_2","stat_3","stat_4","stat_5","stat_6") ~ "실험군") %>%
  bold_labels()

theme_gtsummary_compact()
```

## Continuous
<center> **[Table 1.8] descriptive statistics of Neonatal outcome** </center>
```{r}
stby(n_baby_total[,c(3,24,26,27)], n_baby_total$group_s, descr, stat="common") %>%
  tb(order = 3) %>%
  kable(digits=1, format="html")  %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(table.envir = "ctable", font_size = 17, full_width = F)

theme_gtsummary_compact()
```


















