---
title: "OBGY_Project_1_risk_EDA"
author: "노윤지"
date: "2022-11-09"
output: html_document
---

```{r env, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warnings= FALSE)
library(tidyverse)
library(knitr)
library(gtsummary)
library(labelled)
library(summarytools)
library(kableExtra)
library(magrittr)
```

```{r warning = FALSE, message = FALSE}
source("R_code/find_Preg_Date.R")
source("R_code/cohort_preg_date.R")
source("R_code/split_group.R")
source("R_code/project1_dataset.R")
source("R_code/OBGY_Project1_model_dataset.R")
source("R_code/project1_score.R")
```

[연구주제1_risk 모델링 결과](https://docs.google.com/spreadsheets/d/1BNffaL28VkWOjsfqjE2rPWH-lAJwytpbV8AAOCuRmjI/edit#gid=1527220855)<br/>


### **[Graph of Score]*
```{r warning = FALSE, message = FALSE}
q1 <- ggplot(pr1_df_score,aes(x = score)) +
  geom_density(alpha=0.6, adjust = 3) +
  labs(tag = 'All_group')+
  geom_vline(aes(xintercept = mean(score)),
             color= "blue")+
  geom_histogram(aes(y=..density..),alpha=0.5,
                 position="identity")
 

q2 <- ggplot(pr1_df_score,aes(x = score)) +
  geom_density(alpha=0.6, adjust = 3) +
  labs(tag = 'All_group')+
  geom_vline(aes(xintercept = mean(score)),
             color= "blue")+
  geom_histogram(aes(y=..density..),alpha=0.5,
                 position="identity")+
  scale_x_continuous(limits = c(0,20), breaks = c(0,2.5,5,7.5,10,12.5,15,17.5,20))

q1 
q2
```


### **[Table 1.1] Summary of Maternal characteristics**{.tabset}
#### **[Low risk]** 
```{r}
pr1_df_score_low <- pr1_df_score[c(7:21,23:25,41:44)] %>% 
  filter(group_score == "low_risk")

pr1_df_score_low$twin <- pr1_df_score_low$twin %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_low$전자간증 <- pr1_df_score_low$전자간증 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_low$PIH임신중고혈압 <- pr1_df_score_low$PIH임신중고혈압 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_low$고혈압 <- pr1_df_score_low$고혈압 %>% factor(levels = c(0,1), labels = c("No","Yes"))

pr1_df_score_low$산과력_출산력P <-pr1_df_score_low$산과력_출산력P  %>% factor(levels=c(0,1,2,3), labels = c("0","1","2","≥3"))
pr1_df_score_low$산과력_출산력A <-pr1_df_score_low$산과력_출산력A  %>% factor(levels=c(0,1,2,3), labels = c("0","1","2","≥3"))

pr1_df_score_low$저체중아 <- pr1_df_score_low$저체중아 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_low$태아성장지연 <- pr1_df_score_low$태아성장지연 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_low$태반조기박리 <- pr1_df_score_low$태반조기박리 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_low$부인과수술력 <- pr1_df_score_low$부인과수술력 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_low$자궁봉축술 <- pr1_df_score_low$자궁봉축술 %>% factor(levels = c(0,1), labels = c("No","Yes"))

pr1_df_score_low$입원횟수 <- pr1_df_score_low$입원횟수 %>% factor(levels = c(0,1,2,3,4,5,6), labels = c("0","1","2","3","4","5","6"))
pr1_df_score_low$첫투약시기 <- pr1_df_score_low$첫투약시기 %>% factor(levels = c(0,1,2), labels = c("other","28주미만","28to34"))

pr1_df_score_low$age <- pr1_df_score_low$age %>% factor(levels = c(1,2,3), labels = c("35세미만","35to39","40세이상"))
pr1_df_score_low$bmi <- pr1_df_score_low$bmi %>% factor(levels = c(1,2,3,4,5), labels = c("저체중","정상","과체중","비만","초고도비만"))
pr1_df_score_low$입원총기간 <- pr1_df_score_low$입원총기간 %>% factor(levels = c(1,2,3,4,5), labels = c("1day","2day","3day","4to10","over10"))

pr1_df_score_low$GA_week <- as.numeric(pr1_df_score_low$GA_week)
pr1_df_score_low$score <- as.numeric(pr1_df_score_low$score)

var_label(pr1_df_score_low) <- list(project1_group = "Group(control/test)", age = "Age", GA_week = "Gestational wks of delivery", twin = "Twin", 산과력_출산력P = "Parity P", 산과력_출산력A = "Parity A")


print(dfSummary(pr1_df_score_low, plain.ascii = FALSE, style = "multiline", graph.magnif = 0.75, varnumbers=FALSE, valid.col = TRUE, display.labels=TRUE,
                headings=FALSE), method = 'render')
```

#### **[High risk]** 
```{r}
pr1_df_score_high <- pr1_df_score[c(7:21,23:25,41:44)] %>% 
  filter(group_score == "high_risk")

pr1_df_score_high$twin <- pr1_df_score_high$twin %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_high$전자간증 <- pr1_df_score_high$전자간증 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_high$PIH임신중고혈압 <- pr1_df_score_high$PIH임신중고혈압 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_high$고혈압 <- pr1_df_score_high$고혈압 %>% factor(levels = c(0,1), labels = c("No","Yes"))

pr1_df_score_high$산과력_출산력P <-pr1_df_score_high$산과력_출산력P  %>% factor(levels=c(0,1,2,3), labels = c("0","1","2","≥3"))
pr1_df_score_high$산과력_출산력A <-pr1_df_score_high$산과력_출산력A  %>% factor(levels=c(0,1,2,3), labels = c("0","1","2","≥3"))

pr1_df_score_high$저체중아 <- pr1_df_score_high$저체중아 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_high$태아성장지연 <- pr1_df_score_high$태아성장지연 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_high$태반조기박리 <- pr1_df_score_high$태반조기박리 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_high$부인과수술력 <- pr1_df_score_high$부인과수술력 %>% factor(levels = c(0,1), labels = c("No","Yes"))
pr1_df_score_high$자궁봉축술 <- pr1_df_score_high$자궁봉축술 %>% factor(levels = c(0,1), labels = c("No","Yes"))

pr1_df_score_high$입원횟수 <- pr1_df_score_high$입원횟수 %>% factor(levels = c(0,1,2,3,4,5,6), labels = c("0","1","2","3","4","5","6"))
pr1_df_score_high$첫투약시기 <- pr1_df_score_high$첫투약시기 %>% factor(levels = c(0,1,2), labels = c("other","28주미만","28to34"))

pr1_df_score_high$age <- pr1_df_score_high$age %>% factor(levels = c(1,2,3), labels = c("35세미만","35to39","40세이상"))
pr1_df_score_high$bmi <- pr1_df_score_high$bmi %>% factor(levels = c(1,2,3,4,5), labels = c("저체중","정상","과체중","비만","초고도비만"))
pr1_df_score_high$입원총기간 <- pr1_df_score_high$입원총기간 %>% factor(levels = c(1,2,3,4,5), labels = c("1day","2day","3day","4to10","over10"))

pr1_df_score_high$GA_week <- as.numeric(pr1_df_score_high$GA_week)
pr1_df_score_high$score <- as.numeric(pr1_df_score_high$score)

var_label(pr1_df_score_high) <- list(project1_group = "Group(control/test)", age = "Age", GA_week = "Gestational wks of delivery", twin = "Twin", 산과력_출산력P = "Parity P", 산과력_출산력A = "Parity A")


print(dfSummary(pr1_df_score_high, plain.ascii = FALSE, style = "multiline", graph.magnif = 0.75, varnumbers=FALSE, valid.col = TRUE, display.labels=TRUE,
                headings=FALSE), method = 'render')
```


### **[Table 1.2] Summary of Neonatal outcome**{.tabset}
#### **Low risk**
```{r}
n_baby_pr1_low<-  n_baby_score[c(2:5,10,13:18,29:31,41:43,52:55,71,80,85:86,96:97,38:39,109)] %>% 
  filter(group_score == "low_risk")

n_baby_pr1_low$유도분만 <-n_baby_pr1_low$유도분만 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_low$성별 <-n_baby_pr1_low$성별 %>% factor(levels=c(0,1), labels =c("Female","Male"))
n_baby_pr1_low$분만형태_코드 <- n_baby_pr1_low$분만형태_코드 %>% factor(levels =c(0,1), labels = c("No", "Yes"))
n_baby_pr1_low$병실 <- n_baby_pr1_low$병실 %>% factor(levels =c(0,1), labels = c("No", "Yes"))

n_baby_pr1_low$Apgar.Score1_v2 <-n_baby_pr1_low$Apgar.Score1_v2  %>% factor(levels=c(0,1), labels =c("No(<7)","Yes(≥7)")) 
n_baby_pr1_low$Apgar.Score5_v2 <-n_baby_pr1_low$Apgar.Score5_v2 %>% factor(levels=c(0,1), labels =c("No(<7)","Yes(≥7)"))

n_baby_pr1_low$PROM <-n_baby_pr1_low$PROM %>%factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_low$태변착색 <-n_baby_pr1_low$태변착색 %>%factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_low$True.knot <-n_baby_pr1_low$True.knot %>%factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_low$Nuchal.cord <-n_baby_pr1_low$Nuchal.cord %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_low$산소흡입 <-n_baby_pr1_low$산소흡입 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_low$심폐소생술.유무 <-n_baby_pr1_low$심폐소생술.유무 %>% factor(levels=c(0,1), labels =c("No","Yes"))

n_baby_pr1_low$치료결과 <-n_baby_pr1_low$치료결과 %>% factor(levels=c("48시간 이내사망", "48시간 이후사망", "경쾌", "완쾌", "진단만", "치료안함", "호전안됨"), labels =c("48시간 이내사망", "48시간 이후사망", "경쾌", "완쾌", "진단만", "치료안함", "호전안됨"))

n_baby_pr1_low$출생시체중 <-as.numeric(n_baby_pr1_low$출생시체중)
n_baby_pr1_low$재원기간  <-as.numeric(n_baby_pr1_low$재원기간)


var_label(n_baby_pr1_low) <- list(project1_group = "Group", Apgar.Score1_v2 = "apgar score≥7 (1min)", Apgar.Score5_v2="apgar score≥7 (5min)", 
                          출생시체중 = "출생시체중(kg)", 병실 = "NICU입원여부", 분만형태_코드 = "c/sec 유무")

print(dfSummary(n_baby_pr1_low, plain.ascii = FALSE, style = "multiline", graph.magnif = 0.75, varnumbers=FALSE, valid.col = TRUE, display.labels=TRUE,
                headings=FALSE), method = 'render')
```

#### **High risk**
```{r}
n_baby_pr1_high<-  n_baby_score[c(2:5,10,13:18,29:31,41:43,52:55,71,80,85:86,96:97,38:39,109)] %>% 
  filter(group_score == "high_risk")

n_baby_pr1_high$유도분만 <-n_baby_pr1_high$유도분만 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_high$성별 <-n_baby_pr1_high$성별 %>% factor(levels=c(0,1), labels =c("Female","Male"))
n_baby_pr1_high$분만형태_코드 <- n_baby_pr1_high$분만형태_코드 %>% factor(levels =c(0,1), labels = c("No", "Yes"))
n_baby_pr1_high$병실 <- n_baby_pr1_high$병실 %>% factor(levels =c(0,1), labels = c("No", "Yes"))

n_baby_pr1_high$Apgar.Score1_v2 <-n_baby_pr1_high$Apgar.Score1_v2  %>% factor(levels=c(0,1), labels =c("No(<7)","Yes(≥7)")) 
n_baby_pr1_high$Apgar.Score5_v2 <-n_baby_pr1_high$Apgar.Score5_v2 %>% factor(levels=c(0,1), labels =c("No(<7)","Yes(≥7)"))

n_baby_pr1_high$PROM <-n_baby_pr1_high$PROM %>%factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_high$태변착색 <-n_baby_pr1_high$태변착색 %>%factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_high$True.knot <-n_baby_pr1_high$True.knot %>%factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_high$Nuchal.cord <-n_baby_pr1_high$Nuchal.cord %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_high$산소흡입 <-n_baby_pr1_high$산소흡입 %>% factor(levels=c(0,1), labels =c("No","Yes"))
n_baby_pr1_high$심폐소생술.유무 <-n_baby_pr1_high$심폐소생술.유무 %>% factor(levels=c(0,1), labels =c("No","Yes"))

n_baby_pr1_high$치료결과 <-n_baby_pr1_high$치료결과 %>% factor(levels=c("48시간 이내사망", "48시간 이후사망", "경쾌", "완쾌", "진단만", "치료안함", "호전안됨"), labels =c("48시간 이내사망", "48시간 이후사망", "경쾌", "완쾌", "진단만", "치료안함", "호전안됨"))

n_baby_pr1_high$출생시체중 <-as.numeric(n_baby_pr1_high$출생시체중)
n_baby_pr1_high$재원기간  <-as.numeric(n_baby_pr1_high$재원기간)


var_label(n_baby_pr1_high) <- list(project1_group = "Group", Apgar.Score1_v2 = "apgar score≥7 (1min)", Apgar.Score5_v2="apgar score≥7 (5min)", 
                          출생시체중 = "출생시체중(kg)", 병실 = "NICU입원여부", 분만형태_코드 = "c/sec 유무")

print(dfSummary(n_baby_pr1_high, plain.ascii = FALSE, style = "multiline", graph.magnif = 0.75, varnumbers=FALSE, valid.col = TRUE, display.labels=TRUE,
                headings=FALSE), method = 'render')
```



### **[Table 1.3] **descriptive statistics of Maternal characteristics** {.tabset}

#### **low_risk**{.tabset}
##### **[All group]**
```{r}
theme_gtsummary_compact()

pr1_df_score_low %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[1st_group]**
```{r}
pr1_df_score_low_1 <- pr1_df_score_low %>% 
  filter(project1_sub_group == "1st_group")

pr1_df_score_low_1 %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[2nd_group]**
```{r}
pr1_df_score_low_2 <- pr1_df_score_low %>% 
  filter(project1_sub_group == "2nd_group")

pr1_df_score_low_2 %>%  
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[3rd_group]**
```{r}
pr1_df_score_low_3 <- pr1_df_score_low %>% 
  filter(project1_sub_group == "3rd_group")

pr1_df_score_low_3 %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[4th_group]**
```{r}
pr1_df_score_low_4 <- pr1_df_score_low %>% 
  filter(project1_sub_group == "4th_group")

pr1_df_score_low_4 %>%  
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

#### **high_risk**{.tabset}
##### **[All_group]**
```{r}
pr1_df_score_high %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[1st_group]**
```{r}
pr1_df_score_high_1 <- pr1_df_score_high %>% 
  filter(project1_sub_group == "1st_group")

pr1_df_score_high_1 %>%  
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[2nd_group]**
```{r}
pr1_df_score_high_2 <- pr1_df_score_high %>% 
  filter(project1_sub_group == "2nd_group")

pr1_df_score_high_2 %>%  
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[3rd_group]**
```{r}
pr1_df_score_high_3 <- pr1_df_score_high %>% 
  filter(project1_sub_group == "3rd_group")

pr1_df_score_high_3 %>%  
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```


### **[Table 1.4] **descriptive statistics of Neonatal outcome** {.tabset}

#### **low_risk**{.tabset}
##### **[All_group]**
```{r}
n_baby_pr1_low  %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[1st_group]**
```{r}
n_baby_pr1_low_1 <- n_baby_pr1_low %>% 
  filter(project1_sub_group == "1st_group")

n_baby_pr1_low_1  %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[2nd_group]**
```{r}
n_baby_pr1_low_2 <- n_baby_pr1_low %>% 
  filter(project1_sub_group == "2nd_group")

n_baby_pr1_low_2  %>%
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[3rd_group]**
```{r}
n_baby_pr1_low_3 <- n_baby_pr1_low %>% 
  filter(project1_sub_group == "3rd_group")

n_baby_pr1_low_3  %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[4th_group]**
```{r}
n_baby_pr1_low_4 <- n_baby_pr1_low %>% 
  filter(project1_sub_group == "4th_group")

n_baby_pr1_low_4  %>%
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

#### **high_risk**{.tabset}
##### **[All_group]**
```{r}
n_baby_pr1_high  %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[1st_group]**
```{r}
n_baby_pr1_high_1 <- n_baby_pr1_high %>% 
  filter(project1_sub_group == "1st_group")

n_baby_pr1_high_1  %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[2nd_group]**
```{r}
n_baby_pr1_high_2 <- n_baby_pr1_high %>% 
  filter(project1_sub_group == "2nd_group")

n_baby_pr1_high_2  %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```

##### **[3rd_group]**
```{r}
n_baby_pr1_high_3 <- n_baby_pr1_high %>% 
  filter(project1_sub_group == "3rd_group")

n_baby_pr1_high_3  %>% 
  tbl_summary(by = project1_group, statistic = list(all_continuous() ~ "{mean} ({sd})"),
              missing_text = "(Missing value)", digits = list(all_continuous() ~ c(1, 2), all_categorical() ~ c(0, 1))) %>%
  add_overall() %>%
  add_p(pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  bold_labels()

```
